{\bf {\Large Title....}}

### 2016-07-30 ident_manu.Rnw
state variable factor order changed

# factor levels
cats <- c('Optics', 'Organic Matter', 'Phytoplankton', 'Temperature', 'Zooplankton')
stts_lev <- c('Chla_mg_tot', 'irradiance', 'NH4', 'NO3', 'OM1', 'OM2', 'PO4')
stts_lab <- c('Chlorophyll', 'Irradiance', 'Ammonium', 'Nitrate', 'OM1', 'OM2', 'Phosphate')

@@

<<sensalltile, echo = F, fig.height = 9, fig.width = 9, out.width = '\\textwidth', fig.cap = 'Sensitivity values (L1, \\cref{l1}) for local analyses of all state variables.  Values are truncated by the 5\\textsuperscript{th} and 95\\textsuperscript{th} sensitivity values between all parameters for visual appearance. Parameters are grouped by category (plot strips).  Phytoplankton and zooplankton categories are further separated into one through six, and one and two groups (p1 - p6, z1 - z2), respectively.'>>=
data(sens_ests_cat_all)

@@

stts_lev <- c('Chla_mg_tot', 'irradiance', 'NH4', 'NO3', 'O2', 'OM1', 'OM2', 'PO4')
stts_lab <- c('Chlorophyll', 'Irradiance', 'Ammonium', 'Nitrate', 'Dissolved Oxygen', 'OM1', 'OM2', 'Phosphate')

>>>>

# factor levels
cats <- c('Optics', 'Organic Matter', 'Phytoplankton', 'Temperature', 'Zooplankton')
stts_lev <- c('NH4', 'Chla_mg_tot', 'irradiance', 'NO3', 'OM1', 'OM2', 'PO4')
stts_lab <- c('Ammonium', 'Chlorophyll', 'Irradiance', 'Nitrate', 'OM1', 'OM2', 'Phosphate')

@@

<<sensalltile, echo = F, fig.height = 9, fig.width = 9, out.width = '\\textwidth', fig.cap = 'Sensitivity values (L1, \\cref{l1}) for local analyses of all state variables.  Values are truncated by the 5\\textsuperscript{th} and 95\\textsuperscript{th} sensitivity values between all parameters for visual appearance. Parameters are grouped by category (plot strips).  Phytoplankton and zooplankton categories are further separated into one through six, and one and two groups (p1-p6, z1, z2), respectively.'>>=
data(sens_ests_cat_all)

@@

stts_lev <- rev(c('NH4', 'Chla_mg_tot', 'O2', 'irradiance', 'NO3', 'OM1', 'OM2', 'PO4'))
stts_lab <- rev(c('Ammonium', 'Chlorophyll', 'Dissolved Oxygen', 'Irradiance', 'Nitrate', 'OM1', 'OM2', 'Phosphate'))

### 2016-07-30 ident_manu.tex
state variable factor order changed

\begin{singlespace}
\title{{\bf {\Large Title....}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^1$, John C. Lehrter$^1$}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
	\\{\textit {\normalsize Emails: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}, \href{mailto:lehrter.john@epa.gov}{lehrter.john@epa.gov}}}
  \vspace{1in} 
  \\ Version Date:   Fri Jul 29 17:27:00 2016 -0500
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

@@

\caption{Sensitivity values (L1, \cref{l1}) for local analyses of all state variables.  Values are truncated by the 5\textsuperscript{th} and 95\textsuperscript{th} sensitivity values between all parameters for visual appearance. Parameters are grouped by category (plot strips).  Phytoplankton and zooplankton categories are further separated into one through six, and one and two groups (p1 - p6, z1 - z2), respectively.}\label{fig:sensalltile}
\end{figure}

>>>>

\begin{singlespace}
\title{{\bf {\Large Title....}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^1$, John C. Lehrter$^1$}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
	\\{\textit {\normalsize Emails: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}, \href{mailto:lehrter.john@epa.gov}{lehrter.john@epa.gov}}}
  \vspace{1in} 
  \\ Version Date:   Sat Jul 30 12:31:08 2016 -0500
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

@@

\caption{Sensitivity values (L1, \cref{l1}) for local analyses of all state variables.  Values are truncated by the 5\textsuperscript{th} and 95\textsuperscript{th} sensitivity values between all parameters for visual appearance. Parameters are grouped by category (plot strips).  Phytoplankton and zooplankton categories are further separated into one through six, and one and two groups (p1-p6, z1, z2), respectively.}\label{fig:sensalltile}
\end{figure}
